### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

\stitle{Procedure \identifyaffball}.
Given an $h$-fragmentation ${\cal P}_{h}$ of $P$, $\Delta P$,
(1) it updates \bfc by processing all unit updates in $\Delta P$.
(2) For each $j\in [1, 2^h]$, it then executes a bitwise \kw{AND} operation (\&) between type code $tc_j$ of \fs in \fb and updated filtering code $fc_{j\Delta}$ in \bfc, \ie $tc_j\& fc_{j\Delta}$.
(3) Finally, if $tc_j\& fc_{j\Delta} = fc_{j\Delta}$, \identifyaffball refers to \bs in \fb to mark the balls with type code $tc_j$ as \affballsx, and resets $fc_{j\Delta}$ to $(1, \ldots, 1)$.
This is because \affballsx are balls that have the possibility to match all updated pattern fragments.
The condition $tc_j\& fc_{j\Delta} = fc_{j\Delta}$ holds as long as
(a) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ is 0, \ie there exists an edge/node deletion on ${P}_{fi}$, which may produce more matched nodes, or
(b) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ and $tc_j$ are both 1, \ie  balls with $tc_j$ already match with ${P}_{fi}$, though there are no edge/node deletions on ${P}_{fi}$.

@@

In real-life networks, the quantity of balls with type code ($0,\ldots,0$) is several orders of magnitude larger than that of balls who match with at least one pattern fragment. By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$),
it can reduce a large amount of redundant computations.

>>>>

\stitle{Procedure \identifyaffball}.
Given an $h$-fragmentation ${\cal P}_{h}$ of $P$, $\Delta P$,
(1) it updates \bfc by processing all unit updates in $\Delta P$.
(2) For each $j\in [1, 2^h]$, it then executes a bitwise \kw{AND} operation (\&) between type code $tc_j$ of \fs in \fb and updated filtering code $fc_{j\Delta}$ in \bfc, \ie $tc_j\& fc_{j\Delta}$.
(3) Finally, if $tc_j\& fc_{j\Delta} = fc_{j\Delta}$, \identifyaffball refers to \bs in \fb to mark the balls with type code $tc_j$ as \affballsx, and resets $fc_{j\Delta}$ to $(1, \ldots, 1)$.
%This is because \affballsx are balls that have the possibility to match all updated pattern fragments.
The condition $tc_j\& fc_{j\Delta} = fc_{j\Delta}$ holds as long as
(a) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ is 0, \ie there exists an edge/node deletion on ${P}_{fi}$, which may produce more matched nodes, or
(b) the $i$-th ($i\in [1, h]$) bit of $fc_{j\Delta}$ and $tc_j$ are both 1, \ie  balls with $tc_j$ already match with ${P}_{fi}$, though there are no edge/node deletions on ${P}_{fi}$.

@@

In practice, the number of balls with type code ($0,\ldots,0$) is much larger than those balls matching with at least one pattern fragment. By filtering out balls with \eg $tc$ = ($0,\ldots,0$) or ($1,0,\ldots,0$),
 redundant computations are avoid.
